|

### 2022-12-12 r-report/Paper.Rmd
Text eingefügt und graphen bis 3.2

TO BE DONE: Intro statement.

@@

```{r,fig.cap="Figure 4"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 5"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

### Discussion

@@

```{r,fig.cap="Figure 10"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 11"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 12"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 13"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

### Discussion TBD

To sum up, China has a very high responsibility to mitigate climate change, even the highest responsibility of all countries when considering some of the discussed equity metrics. Based on our calculations, China is likely surpass the EU well before 2030 and the US shortly after in 2032  in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter. The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic respon

Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed.

However, we also need to consider that China only ranks on 81st. and 43rd place considering their GDP per capita and their emissions per capita, respectively. This diminishes China’s responsibility to some extent, showing that the global community needs to grant space for economic development to be fair. However, this economic development should ideally be decoupled from a growth in emissions. If we look at the per capita emissions of the countries that rank first, we see that these are mostly very small and, from the perspective of absolute emissions, less important countries. Although these countries might have a high ability to pay from a per capita perspective, their overall economic power is not high. The opposite is true for China. China ranks first place in absolute emissions and GDP in 2019 with a great distance to the following places.

Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.

@@

Our analysis of different equity metrics for the second research question has shown that China not only has a huge responsibility to curb emissions, but also the financial capability to do so. The country is the world’s largest emitter in annual and cumulative terms (based on our data) and has the highest GDP of all countries. While it is important to acknowledge further room for development, one cannot disregard the fact that without significant emission reductions from China, any attempt to stay within the temperature limits of the Paris Agreement is sure to fail.

@@

In the following, our analysis will be contrasted with two other assessments of China’s fair share – the assessment by the Climate Action Tracker and by the Climate Equity Monitor.

@@

Another equity metric is developed by the Climate Equity Monitor. The Climate Equity Monitor is the first initiative from the Global South that tracks equity in climate action for Annex 1 and Non-Annex 1 countries. The initiative calculates the fair share of the carbon budget by using the share of cumulative emissions based on the share in the global population for a contemporary base year (2019). The cumulative annual emissions of a country are calculated for the period from 1850 to 2019. Based on this, the Climate Equity Monitor calculates if a country has a carbon debt or carbon credit. This measure is calculated as the difference between cumulative emissions of a country and the country’s fair share of the global carbon budget already consumed. For China as a Non-Annex 1 country, they conclude that the country has a carbon credit of 122.4 Gt CO2eq. In comparison, India has a carbon credit of 337.6 Gt CO2eq while the US has a carbon debt of 445 Gt CO2eq, and Russia has a carbon debt of 125.44 Gt CO2eq [@CEM2022]. Accordingly, if China kept emitting at its current rate, it would have used up its remaining carbon credit until 2031.

@@

Our analysis has the following limitations: We only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable. The problem of climate change caused by anthropogenic greenhouse gas emissions has only been known since the 1970s, and since the 1990s there has been a dedicated international process to address the problem. Against this background, an additional consideration of cumulative emissions in these time periods might be worthwhile. For a comprehensive assessment of China’s fair share, it would have also been interesting to discuss further equity metrics such as a ranking of consumption-based emissions. However, this was not possible for us, as our data only included consumption-based data for approx. 100 countries and crucially missing the US, making a comparison less meaningful.

>>>>

The following sections will detail our analysis with regard to the two research questions. We first turn to China's self-categorization as developing country and contrast it with different comparisons of development metrics as well as emission trends. After an interim discussion we will look at China's responsibility with regard to (projected) cumulative emissions and construct rankings for different equity metrics.

@@

```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 201
COUNTRY = "China"
GAS = "GHG"

source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_kaya_country_vs.developed-vs_developing.R", local = TRUE, print.eval = TRUE)

@@

```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

source("r-analysis/data_kaya_analysis.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_kaya_incomelevels.R", local = TRUE, print.eval = TRUE)

@@

### Section Summary

@@

```{r,fig.cap="Figure 10: Absolute GHG Emission - 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_ranking_abs.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_rank_abs.R", local = TRUE, print.eval = TRUE)

@@

```{r,fig.cap="Figure 11: Per Capita Emissions- 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_ranking_per_cap.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_rank_pc.R", local = TRUE, print.eval = TRUE)

@@

```{r,fig.cap="Figure 12: Absolute GDP p - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_rank_gdp.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_rank_gdp.R", local = TRUE, print.eval = TRUE)

@@

```{r,fig.cap="Figure 13: GDP per Capita - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

source("r-analysis/data_rank_gdp_pc.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_rank_gdp_pc.R", local = TRUE, print.eval = TRUE)

@@

### Section Summary

To sum up, China has a very high responsibility to mitigate climate change, even the highest responsibility of all countries when considering some of the discussed equity metrics. Based on our calculations, China is likely to surpass the EU well before 2030 and the US shortly after in 2032 in terms of cumulative emissions over all GHGs from 1850 to 2019 and a modeling of emissions thereafter. The difference in emissions from all GHGs to CO2 emissions highlights the importance to extend the frame of historic responsibility beyond CO2 emissions –  especially in light of growing capabilities, issue salience and data availability that all put greater responsibility recent emissions. 
Therefore, China now has a major responsibility to reduce emissions which is reinforced when considering that the country’s massive emissions growth only started after the adoption of the Kyoto Protocol in 1997, at a time when the consequences of climate change were already being heavily discussed. 
However, we also need to consider that China only ranks on 81st and 43rd place considering their GDP per capita and their emissions per capita, respectively. This diminishes China’s responsibility to some extent, showing that the global community needs to grant space for economic development to be fair. However, this economic development should ideally be decoupled from a growth in emissions. If we look at the per capita emissions of the countries that rank first, we see that these are mostly very small and, from the perspective of absolute emissions, less important countries. Although these countries might have a high ability to pay from a per capita perspective, their overall economic power is not high. The opposite is true for China. China ranks first place in absolute emissions and GDP in 2019 with a great distance to subsequent ranks. 
Thus, China has one of the greatest responsibilities to reduce emissions from a historic emissions, current emissions and economic capacity perspective.

@@

Our analysis of different equity metrics for the second research question has shown that China not only has a huge responsibility to curb emissions, but also the financial capability to do so. The country is the world’s largest emitter in annual terms , on a pathway to take the first  position in  cumulative terms within a decade and has the highest GDP of all countries. While it is important to acknowledge the need for further economic development, one cannot disregard the fact that without significant emission reductions from China, any attempt to stay within the temperature limits of the Paris Agreement is sure to fail.

@@

In the following, our analysis will be contrasted with two other assessments of China’s responsibility – the assessment by the Climate Action Tracker and by the Climate Equity Monitor.

@@

Another equity metric is developed by the Climate Equity Monitor. The Climate Equity Monitor is the first initiative from the Global South that tracks equity in climate action for Annex 1 and Non-Annex 1 countries. The initiative calculates the fair share of the carbon budget by using the share of cumulative emissions based on the share in the global population for a contemporary base year (2019). The cumulative annual emissions of a country are calculated for the period from 1850 to 2019. Based on this, the Climate Equity Monitor calculates whether a country has a carbon debt or carbon credit. This measure is calculated as the difference between cumulative emissions of a country and the country’s fair share of the global carbon budget already consumed. For China as a Non-Annex 1 country, they conclude that the country has a carbon credit of 122.4 Gt CO2eq. In comparison, India has a carbon credit of 337.6 Gt CO2eq while the US has a carbon debt of 445 Gt CO2eq, and Russia has a carbon debt of 125.44 Gt CO2eq  [@CEM2022]. Accordingly, if China kept emitting at its current rate, it would have used up its remaining carbon credit until 2031.

@@

While aiming to be as comprehensive as possible our analysis has some limitations. First, we only consider cumulative emissions from 1850-2019, but the consideration of other time periods could also be conceivable. The problem of climate change caused by anthropogenic greenhouse gas emissions has only been known since the 1970s, and since the 1990s there has been a dedicated international process to address the problem. Against this background, an additional consideration of cumulative emissions in these time periods might be worthwhile. Second, the projection of future emissions rests on major simplification assumptions, it is likely that a more sophisticated approach such as an ARIMA-modelling would result in more robust estimates. Third, a comprehensive assessment of China’s responsibility could discuss further equity metrics such as a ranking of consumption-based emissions. However, this was not possible for us, as our data only included consumption-based data for approx. 100 countries and crucially missing the US, making a comparison less meaningful. Lastly, reducing capacity to mere GDP and GDP per capita considerations is very much simplifying the issue, as land area, access to renewable resources and intellectual property and many other factors determine a countries mitigation potential, which is very likely to differ by sector. 
With these limitations in mind, we believe none the less that our analysis has shed light on the special case of China and has shown that the under complex self-assessment does not withstand a thorough analysis. Keeping these assessments in mind will be worthwhile when assessing the responsibilities of upcoming developing nations. The case of China has shown that it is crucial to come to a mutual understanding of what constitutes responsibilities and how they can assessed on an objective basis. Especially our analysis of future cumulative emissions indicates that it will be key to frame the issue beyond CO2.
